---
title: "VF Sheep"
author: "Jackie"
date: "2022-11-02"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Aim of the trial

Implement VF collars on a commercial farm.
The aim was to ensure the collars work and that they are safe and effective.

Evaluate the cue and pulse data and animal movement during the training period and the trail.

## Location of the trial

Note that we have included a 10m buffer around the paddock boundaries.
And the map displays the buffer for the VF too

The VF trial only had one fence.

```{r map of the paddock boundaries}




```

## Lenegth and dates of the trial
Start of training period 
End of training period

The animals were yarded everyday and during this time collar and health check were performed.
The collars continued to log during this time therefore the data needs to be cropped to reflect the only trial times

Day 1 animals yarded in out
Day 2 animals yarded in out
Day 3 animals yarded in out
Day 4 animals yarded in out
Day 5 animals yarded in out




```{r pressure, echo=FALSE}
plot(pressure)
```

## Animal collar used

Location of the raw data


## Background information on animal collar data from Gallagher

*Contact*

*Data provided*

*TimeofEvent*

*GPS*

*Audio and pulse readings*

*Virtual Fence*

*Animal activity*




## Data manipulation notes.

step 1 
step 2
step 3
